%!Tex root = bare_conf.tex

\section{Introduction}
% no \IEEEPARstart
 
% Popularity of A.I
Artificial intelligence defeated human play in the game `Go'.
As the number of cases in go is considered much larger than the number of cases in chess or Korean chess, go is treated as the unsolvable game to artificial intelligence.
However, AlphaGo defeated Korean top go player Sedol Lee, and the next version of AlphaGo defeated top go player Ke Jie.
Interestingly, AlphaGo decided to put a stone to a strange location that most go players could not understand~\cite{wierd_alphago}.
Many players shocked about the play of the AlphaGo and tried to learn the new strategies.

% Importance of MCTS
Monte Carlo tree search (MCTS) is a decision making algorithm that is used to implement AlphaGo~\cite{silver2016mastering_alphago}.
MCTS requires large number of simulations, and we hypothesized that large number of simulations led AlphaGo to the strange-but-good location.
The larger number of simulations, the better decision MCTS shows.
However, go has time limit for each turn, the number of simulations for each turn must be limited.

% Success of MCTS. Parallelism
AlphaGo put large number of hardware to increase the number of simulations~\cite{silver2016mastering_alphago}.
The paper-version AlphaGo used 48 CPUs and 8 GPUs.
Those hardware computing unit computes each simulation cases in parallel.
The main factor of defeating human is not only improvement of algorithm, but also improvement of hardware.

% Drawback of MCTS.
However, specific case of the game algorithm can harm the parallelism of MCTS.
GPU-based parallelism exploits the SIMT model that executes the same instruction within many threads.
Therefore, branch instruction harms the parallelism because both of taken branch and non-taken branch need to be executed.
The problem is called \textit{branch divergence}, and high \textit{branch divergence} decreases a program's performance drastically.

% Case study by Da Vinci Code
We hypothesized that a board game game 'Da Vinci Code' suffered from branch divergence.
% Not only branch divergence, Da Vinci Code has large number of cases.
The property harm the decision because of two reasons.
Firstly, branch divergence make different length of execution path of each thread, and the shorter-lengthed thread decreased SIMD utilization.
Secondly, branch divergence make large number of MCTS cases, and large number of cases decreased the number of simulations per a case within a fixed time duration.
In Da Vinci Code, each player guess other player's tile.
A player may guess one more tile when the player guessed a tile correctly, and this characteristic makes barnch divergence.
% A player could not know about other player's tile before making a correct dicision, and this randomness makes the number of cases much larger.
We explained the detailed rule of Da Vinci Code~(Section~\ref{sec:davinci}) and interesting features of Da Vinci Code~(Section~\ref{sec:mcts}) later.


% Prove of drawbacks (overhead)
We implement and evaluated two versions of MCTS to compare how branch divergence problem affects performance on GPU.
We implemented CPU-version of MCTS, called \cpu, which used OpenMP to parallelize simulations.
We implemented GPU-version of MCTS, called \gpu, which used CUDA library to parallelize simulations.
We evaluated both of \cpu~and \gpu.
% \cpu shown linear fashion performance increasing, whereas \gpu showed non-linear fashion performance increasing and peformance valley.
% Performance up to 12 threads increases linearly on \cpu.
% Since each core proceeds the thread, performance improvements due to threads increase are limited by the count of cores.
In \cpu~case, each thread is executed by a core, so performance improvement over the number of threads is maintained.
However, in \gpu~case, group of threads are executed by a core (SM or streaming multiprocessor), so performance improvement over the number of threads are not maintained.
We concluded that branch divergence within a warp and memory contention decreases the performance.
Branch divergence which resulted from unbalanced game length makes low scalability.
The performance valley resulted from memory contention as the threads increase. 

% We has found the features which makes performance degradation on \gpu which are memory contention, branch divergence.
% We will analysis the main feature which causes the performance degradation.
% We will optimize \gpu by solving the problems.
% We will utilize shared memory and use memory locality to reduce memory contention.
% In addition, we will modify the branch statement to reduce branch divergence so that there is not an idle thread left.

% Future plan. Future work. (Discussion)


% Intro to rest of the paper

% Monte Carlo Tree Search (MCTS) is a decision making algorithm which has been used for implementing aritifial intelligence(AI) widly.
% Since MCTS is used for games which proceed on real time, it should make decision within a limied time. 
% However, we have to repeat a number of simulated games for good performance of MCTS. 
% If MCTS doesn't have enough simulated games, MCTS can make wrong decision. 
% Therefore parallelism of MCTS not only make right decision, but also reduce the time.\\
% The Da vinci code is the kinds of board game. This game guesses the tiles of opponent based on 

% \hfill mds
 
% \hfill December 23, 2017